\documentclass[12pt,onecolumn]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage[document]{ragged2e}
\usepackage{lastpage}
\newcommand*{\showline}[1][2]{\makebox[#1in]{\hrulefill}}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}
\rhead{}
\rfoot{}
\chead{}
\cfoot{}
\fancyhead[CO]{
 {\LARGE Progress Evaluation Meeting Checklist}}
\fancyfoot[LO]{
 version dated \today \hspace{2pt} pg. \thepage\ of \pageref{LastPage}}

%\usepackage{textcomp}
\usepackage{multicol}
%\usepackage{ulem}
%\usepackage{amssymb}

\begin{document}

{\large
Student: \showline[2.5] \hspace{20pt}
Advisor: \showline\\
Student Entrance Year: \showline[1.5] \hspace{20pt}
Date: \showline[1.5]\\
Committee Members: \showline[3]
Present? \textbf{Y} / \textbf{N}} \vspace{16pt}

{\large
\underline{Progress towards departmental degree requirements:}
\begin{multicols}{2}
\framebox(10,10){} Cumulative exams completed\\
\framebox(10,10){} Classes completed\\
\framebox(10,10){} Class work orals completed\\
\framebox(10,10){} Thesis proposal completed\\
\end{multicols}}

{\large \underline{General discussion guidelines:}}\\
These meetings should be a discussion between the student and faculty on both current student progress and future directions. Students are expected to do a self-evaluation prior to the meeting and lead the discussion in a positive direction. Faculty are expected to be direct, constructive, and communicative. Both are expected to come to a consensus on the future direction of the thesis project, including a detailed timeline.
\vspace{16pt}

{\large \underline{Current progress discussion guidelines:}}\\
Prior to the meeting students should do a self-assessment of their progress in each of the listed areas. Additionally, the discussion should contain constructive comments from the faculty on student progress. This should address both areas where the student is doing well and areas where the student could improve.
\vspace{16pt}

{\large \underline{Future directions discussion guidelines:}}\\
\textit{This portion of the meeting is extremely important and should be addressed in detail. The student and advisor, and to some extent the committee, must agree that this is the plan with which to move forward.}\\
Please give special attention to revising the student timeline 
with updated research goals and milestone dates. In the event of a currently unrealistic timeline for graduation, please discuss the following options a) change the research plan to meet the original defense date or b) change the defense date to match the research plan.\\
\textit{Do not forget to discuss fellowship applications, travel money, and summer funding and research opportunities.}
\vspace{16pt}

{\large
\underline{Action Items:}\\
\begin{enumerate}
\item Student fills out ``Meeting Checklist'' and detailed timeline prior to meeting
\item Advisor reads blank ``Meeting Checklist'' and prepares discussion items for meeting
\item During meeting timeline is adjusted and signed off upon by advisor 
and committee, including details and defense date
\end{enumerate}}

\newpage


{\large
\underline{Progress towards research goals}}
\begin{itemize}
\item Discussion of research progress and individual project goals. This may include 
adjustment of thesis project to meet currently realistic goals.
\end{itemize}

\textsc{Current Progress}\\ \vspace{36pt}
\textsc{Future Directions}\\ \vspace{42pt}

{\large
\underline{Conference attendance and presentations}}
\begin{itemize}
\item Is conference attendance too frequent/infrequent? Is conference content  appropriate (too specialized/general)? Are funds available to attend conferences? Also discuss the \emph{quantity} and \emph{quality} of presentations given (i.e. advice to improve posters/talks) and networking skills.
\end{itemize}

\textsc{Current Progress}\\ \vspace{36pt}
\textsc{Future Directions}\\ \vspace{42pt}

{\large
\underline{Literature knowledge}}
\begin{itemize}
\item i.e. knowledgeable, appropriate, poor. Explain.
\end{itemize}

\textsc{Current Progress}\\ \vspace{24pt}
\textsc{Future Directions}\\ \vspace{36pt}

{\large
\underline{Paper writing}}
\begin{itemize}
\item Include discussion of number of papers completed and expected to be completed before graduation, quality of writing, and speed of progress.
\end{itemize}

\textsc{Current Progress}\\ \vspace{36pt}
\textsc{Future Directions}\\ \vspace{42pt}

\newpage


{\large
\underline{Skills assessment}}\\
\textsc{time management:}\\
\textsc{autonomy:}\\
\textsc{leadership:}\\
\textsc{collaboration:}\\
\textsc{organization:}\\
\textsc{initiative:}\\
\vspace{16pt}

{\large
\underline{Other comments}}
\begin{itemize}
\item i.e. teaching ability, outreach, other skills, etc.
\end{itemize}
\vspace{72pt}


{\large
\underline{Timeline}}
\begin{itemize}
\item Discussion and re-evaluation of current timeline. Write out detailed timeline using front and back including conference attendance, publishing papers, submitting job applications, and thesis defense date.
\end{itemize}

\newpage
{\large
\underline{Timeline continued}}

\end{document}
